\Huge Stellar continuum modelling

### 2023-12-06 paper/main.tex
beer oclock

\newcommand{\project}[1]{\textit{#1}}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\vectheta}{\boldsymbol{\theta}}
\newcommand{\vecpsi}{\boldsymbol{\psi}}
\newcommand{\vecW}{\mathbf{W}}
\newcommand{\vecH}{\mathbf{H}}
\newcommand{\vecV}{\mathbf{V}}
\newcommand{\hadamard}{\odot}

@@

- choice of grid
- regions for continuum modelling

The continuum-instrument response of the APOGEE detector was modelled using a 3 degree sines-and-cosines with a length-scale $L = 1300$, but allowing for different coefficients per chip.

- choices of iterations, initialisation, etc, 
- eigenspectra examples already shown

@@

Code is available at \url{https://github.com/andycasey/continuum} and is registered in the Python Package Index as \texttt{stellar-continuum}.

>>>>

\newcommand{\project}[1]{\textit{#1}}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\vectheta}{\boldsymbol{\theta}}
\newcommand{\vecpsi}{\boldsymbol{\psi}}
\newcommand{\vecW}{\mathbf{W}}
\newcommand{\vecH}{\mathbf{H}}
\newcommand{\vecV}{\mathbf{V}}
\newcommand{\hadamard}{\odot}
\newcommand{\apogee}{\project{APOGEE}}
\newcommand{\boss}{\project{BOSS}}

@@

The \apogee\ spectrograph spans approximately 1.5 to 1.7\,microns and has a resolving power of about 22,500 \citep{wilson}. There are three chips, which we chose to model as separate continuum regions (each with their own continuum coefficients $\vecpsi$). We used a 3rd order sine-and-cosine basis with length scale $L = 1300$, corresponding to 7 continuum coefficients per chip.

We use the \todo{DR17 grids computed for FERRE, some in non-LTE}. The data are assumed to be resampled onto a rest-frame wavelength sampling that is uniform in log-spacing. We took the high-resolution theoretical grids and convolved them to a spectral resolution of 22,500 and sampled it to match the data. In total there are nearly \todo{1 M} spectra each with 8,575 pixels. This proved too large to fit in memory when computing the eigenspectra $\vecH$, forcing us to skip every 10th spectra.

We chose to use 32 eigenspectra to construct the line absorption model, some of which are shown in Figure~\ref{fig:schematic}. During training, the hydrogen lines separate out immediately before other absorption features are recognizable. The final eigenspectra include multiple hydro \todo{BEER OCLOCK}

@@

%Code is available at \url{https://github.com/andycasey/continuum} and is registered in the Python Package Index as \texttt{stellar-continuum}.
